Towards Compiler-Agnostic Performance in Finite-Difference Codes. (TBC)

### 2014-11-19 docs/papers/shallow_performance/shallow_perf.tex
More text on the psykal structure of shallow

In order to maximise the flexibility (and thus potential for
optimisation) of the \psykal version of shallow, we made the kernels
as fine-grained as possible. In this case, this resulted in eight
distinct kernels, each of which operated on a single field at a single
point (since we have chosen to use point-wise kernels).

>>>>

In order to maximise the flexibility (and thus potential for
optimisation) of the \psykal version of shallow, we made the kernels
as fine-grained as possible. In this case, this resulted in eight
distinct kernels, each of which operated on a single field at a single
point (since we have chosen to use point-wise kernels). With a little
bit of tidying/re-structuring, we found it was possible to express the
contents of the main time-stepping loop as a single invoke (a call to
the PSy layer) and a call to the I/O system
(Figure~\ref{FIG_psykal_shallow_structure}). The single PSy-layer
routine then consists of applying each of the kernels to all of the
points on the model mesh requiring an update.

{\bf How we handle the PBCs.}
